Neural dialogue act recognition with transformer pre-training

### 2019-04-07 abstract.tex
laughters -> laughter

  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for DAR, additional information only present in natural dialogue data will be useful. In SWDA disfluencies are annotated and for the datasets where no annotation for disfluencies is available, they can be predicted from recognized speech \citep{hough2017joint,shalyminov2018multi}. We evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models and suggest the ways to include information about disfluencies in pre-trained models.

>>>>

  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for DAR, additional information only present in natural dialogue data will be useful. In SWDA disfluencies are annotated and for the datasets where no annotation for disfluencies is available, they can be predicted from recognized speech \citep{hough2017joint,shalyminov2018multi}. We evaluate the impact of disfluencies and non-verbal signals, such as laughter, on the performance of our models and suggest the ways to include information about disfluencies into pre-trained neural models.
